%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Jobs \& Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\textbf{Software Development Engineer Intern}} % Job title
    {Amazon Web Services \href{https://aws.amazon.com/}{\faExternalLink}} % Organization
    {Jun 2021 - Sep 2021} % Location
    {\textbf{Berlin, Germany}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on performance improvements for the {\textbf{Amazon Lookout for Metrics \href{https://aws.amazon.com/lookout-for-metrics/}{\faExternalLink}}} service.}
        \item {Decreased memory consumption of the training workflow by \textbf{\~{}93\%} and allowed a potential throughput increase from \textbf{50K time series to 1M time series}, by developing a pre-processing phase that converts datasets into a more efficient format.}
        \item {Performed extensive testing and performance benchmarking, in order to report execution times, memory consumption and CPU usage.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\textbf{Research Assistant - "Big Data for Energy"}} % Job title
    {INESC TEC \href{https://www.inesctec.pt/en}{\faExternalLink}} % Organization
    {Feb 2020 - May 2021} % Location
    {\textbf{Porto, Portugal}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a platform to foster energy analytics for R\&D institutions, by automating energy and weather data collection and management.}
        \item {Automated energy data collection by making scripts that periodically fetch data from APIs of electricity data sources in Europe.}
        \item {Implemented missing values detection by developing a module that monitors DB with 130+ tables, each one with an average of 3 million rows.}
        \item {Allowed registered users to extract desired data by building an authentication layer and a REST API, and by helping create a user interface.}
        \item {Main technologies used: \textbf{Python, Django, Pandas, Apache Cassandra, RabbitMQ, Celery, Nginx, Vue.js, Docker, GitLab CI/CD.}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
     {\textbf{Teaching Assistant}} % Job title
    {Faculty of Engineering of the University of Porto (FEUP) \href{https://sigarra.up.pt/feup/pt/web_page.inicial}{\faExternalLink}} % Organization
    {Feb 2021 - May 2021} % Location
    {\textbf{Porto, Portugal}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped students in the \textbf{IART - Artificial Intelligence} subject with search and optimization algorithms, and Machine Learning exercises.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {\textbf{Software Engineer Intern}} % Job title
    {Critical Software \href{https://www.criticalsoftware.com/en}{\faExternalLink}} % Organization
    {Jul 2020} % Location
    {\textbf{Coimbra, Portugal}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learned about the methodologies and tools used in critical projects, such as software for airplanes, trains and banks.}
        \item {Built a real time chat service using \textbf{Java} and \textbf{Kafka}, and an encryption/decryption system for smart meter data with \textbf{Java}, \textbf{SSL} and \textbf{XML}.}
      \end{cvitems}
    }


%---------------------------------------------------------

%\cventry
%     {\textbf{NIAEFEUP - Informatics Engineering Student Branch @ FEUP \href{https://ni.fe.up.pt/}{\faExternalLink}}} % Job title
%    {Active Member} % Organization
%    {Nov 2019 - Present} % Location
%    {\textbf{Porto, Portugal}} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Participated in and organized a variety of events/projects in different areas, ranging from Cybersecurity to AI to Competitive Programming.}
%        \item {Organized and presented a Git, GitHub and Open Source contributions workshop for 20+ students.}
%      \end{cvitems}
%    }

\end{cventries}
